\documentclass[journal.tex]{subfiles}

\usepackage{tikz}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{algpseudocode}
\usepackage{algorithm}

% Add vertical spacing to tables
\renewcommand{\arraystretch}{1.4}

% Begin Document
\begin{document}

\pagebreak
\section*{February 10, 2022}

Today's class was centered around the activity of using a writing prompt to tell a story.
The prompt was fairly simple, and very open ended, leaving room for a lot of creativity.
I ended up going with a fiction, sci-fi themed story of a captain with illicit cargo.

After we wrote our story, we swapped the opening line and prompt with a classmate.
Then we wrote a story based off their opening line and interpretation of the prompt.
This was followed with comparing the stories each wrote about their prompts.

This was done in order to explore the different motivations and purposes for writing.
We each wrote with a specific audience in mind.
I wrote a fiction work, targeting people that are familiar with the themes and ideas of science fiction.
My partner used my same prompt, and turned it into a story about baking cookies.

The stories took a different philosophical approach, as mine explored the actions and left open character development for the character.
My partner's was more focused on the doubt a person has when working hard on a new skill, and the feelings that come from finding success.
I believe it to be a bit more of a reflective piece by the author, with a lot of emotions probably ones that the author has explored personally.


\end{document}